Incentivizing Exploration by Heterogeneous Users

### 2018-02-17 abstract.tex

We consider the problem of incentivized exploration with heterogeneous agents.
In this problem, bandit arms provide vector-valued outcomes equal to an unknown
arm-specific attribute vector perturbed by independent normally distributed
noise.  Agents arrive sequentially and choose arms to pull based on their own
private and heterogeneous linear utility function over attributes and estimates
of the arms' attribute vectors derived from observations of other agents' past
pulls.  Agents are myopic and selfish and thus would choose the arm with
maximal estimated utility, except for an incentive payment that a principal may
offer to encourage agents to explore underplayed arms.  The principle seeks to
minimize the expected cumulative regret incurred by agents relative to their
best arms, while also making a small expected cumulative payment.  We propose
an algorithm that incentivizes arms played infrequently in the
past whose probability of being played in the next round would be small
without incentives.  Under the assumption that each arm is preferred by at
least a fraction $p>0$ of agents, we show this algorithm achieves expected
cumulative regret of $O(N\exp(2/p) + N \log(T)^3)$ using expected cumulative
payments of $O(N^2 \exp(2/p))$.  If $p$ is known or the distribution over agent
preferences is discrete, the term $\exp(2/p)$ can be eliminated.  In these
cases, the bound on payment improves to $O(N^2 / p^{5/2})$.  The bound on
regret improves to $O(N/p^4 + N^2/p^2 + N \log(T)^3 / p)$ for known $p$ and to
$O(N/p^4 + N^2/p^2)$ for discrete preference distributions.  Regret and
payments that are both constant in $T$ for discrete preferences stands
in contrast to the $\log(T)$ dependence on regret in standard multi-armed bandit
problems, and arises because heterogeneity in agent preferences allows
exploitation of arms to also explore fully.

>>>>

We consider the problem of incentivizing exploration with heterogeneous agents.
In this problem, bandit arms provide vector-valued outcomes equal to an unknown
arm-specific attribute vector,
perturbed by independent normally distributed noise.
Agents arrive sequentially and choose arms to pull based on their own
private and heterogeneous linear utility functions over attributes
and the estimates of the arms' attribute vectors derived from
observations of other agents' past pulls.
Agents are myopic and selfish and thus would choose the arm with
maximum estimated utility.
A principal, knowing only the distribution from which agents'
preferences are drawn, but not the specific draws,
can offer incentive payments for pulling specific arms
in order to encourage agents to explore underplayed arms.
The principal seeks to minimize the total expected cumulative regret
incurred by agents relative to their best arms,
while also making a small expected cumulative payment.

We propose an algorithm that incentivizes arms played infrequently in the
past whose probability of being played in the next round would be small
without incentives.
Under the assumption that each arm is preferred by at
least a fraction $\MinProb > 0$ of agents,
we show that this algorithm achieves expected
cumulative regret of $O (\ARMNUM \e^{2/\MinProb} + \ARMNUM \log^3(T))$,
using expected cumulative payments of $O(\ARMNUM^2 \e^{2/\MinProb})$.
If \MinProb is known or the distribution over agent
preferences is discrete,
the exponential term $\e^{2/\MinProb}$ can be replaced with suitable
polynomials in \ARMNUM and $1/\MinProb$.
For discrete preferences, the regret dependence on $T$ can be
eliminated entirely, giving constant (depending only polynomially on
\ARMNUM and $1/\MinProb$) expected regret and payments.
This constant regret stands in contrast to the $\Theta(\log(T))$ dependence of
regret in standard multi-armed bandit problems.
It arises because even unobserved heterogeneity in agent preferences
allows exploitation of arms to also explore arms fully;
succinctly, heterogeneity provides free exploration.
